Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-11-28 MHCpaper/MHCsupp.tex
Paragraph about balanced pot ready
temp balanced cascade fig

We see that, for most parameter values, such models do not reproduce the observed learning impairment with enhanced plasticity.
In some cases a very small learning impairment was seen ($\CO(10^{-5})$), but these occurred at extreme parameter values where the tolerances used in fitting the potentiation parameter could have a noticeable impact.

>>>>

%We see that, for most parameter values, such models do not reproduce the observed learning impairment with enhanced plasticity.
%In some cases a very small learning impairment was seen ($\CO(10^{-5})$), but these occurred at extreme parameter values where the tolerances used in fitting the potentiation parameter could have a noticeable impact.

We see that, for all parameter values, such models do not reproduce the observed learning impairment with enhanced plasticity.
The normal baseline oculomotor performance must have some other explanation, such as those outlined in \compfig.
